---
title: "Agreement between Co-oximetry and Cynohemoglobinometry in Hemogobin Measurements"
description: |
  
author:
  - name: Idris Chikophe
    affiliation: Aga Kahn University Hospital
journal: 
  title: "Journal of Anesthesia and Critical Care"
  issn: 2490-1752
  publisher: Xtreme Gradient Press
volume: 10
issue: 4
doi: "10.23915/distill.00010"
slug: jones2018distill
    
date: 2023-12-12
output:
  distill::distill_article:
    toc: true
    toc_depth: 3
    toc_float: true
    self_contained: false
---


```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(readr)
library(gtsummary)
library(ggstatsplot)
```


# Abstract

## Introduction

Critical care medicine relies heavily on accurate and timely monitoring of a patient's hemoglobin (Hb) levels to guide treatment decisions. Point of care hemoglobin (SpHb) measurement devices have gained popularity due to their non-invasive nature and ability to provide real-time Hb values, potentially reducing the need for frequent blood draws. However, the agreement of SpHb measurements with traditional Coulter Hb measurements remain subjects of concern and investigation.

## Objective

The primary objective of this study was to assess and establish the agreement between SpHb measurements and Coulter Hb measurements in critically ill patients.

## Materials and Methods

This was a cross-sectional observational study conducted in the intensive care unit (ICU) of BigsBy Hospital over a period of 12 months. A total of 200 critically ill adult patients requiring continuous Hb monitoring were be enrolled in the study. SpHb and Coulter Hb measurements were performed simultaneously using standard laboratory methods. 

Bland-Altman analysis was used to establish the bias, limits of agreement, and generation of Bland-Altman plots.

## Conclusion

The bias was 0.1 g/dL, limits of agreement were +2 or -2. This was in keeping with the American College of Pathologists.


## Results

```{r, include=FALSE}
set.seed(111)
n = 150
sphb <- round(runif(n,8,15),1)
coulter <- round(runif(n,9,17),1)
gender <- sample(c("F","M"), size = n, prob = c(0.35,0.65), replace = T)
data = tibble(gender,sphb,coulter)
head(data)
```

### Table 1: Summary Statistics

```{r, echo=FALSE}
t1 <- data %>% 
  tbl_summary(by=gender) %>% 
  add_overall() %>% 
  add_p()
t1
```
### Visualization

```{r, echo=FALSE}
gathered <- data %>% gather(key="Method", value = "Hb", c(2:3))
ggbetweenstats(data = gathered, x="Method", y="Hb")
```

